Symmetry-based constraints on the size of the dynamical Solar neighborhood

### 2019-04-09 paper/ms.tex
Small changes

If the system being considered departs from axisymmetry in a significant and/or non-adiabatic way, the actions computed using an axisymmetric approximation to the true potential can exhibit cyclic dependence on the orbital phase (or time at which the star's position and velocity are observed), large-scale migration, or diffusion from their initial values.
In the Milky Way, stellar actions are expected to diffuse on short time scales due to scattering with gas clouds
and to evolve on longer time scales in the case of orbits near resonances with spiral arms, bar(s), and other
large scale perturbations \citep{2014RvMP...86....1S}. For this reason, we and
other authors have used actions to study stellar scattering in the Milky Way
disk using the improved astrometry of {\em Gaia} DR2 and various age
catalogues \citep{2018ApJ...867...31B,2018arXiv180803278T}. Actions have also
been used to study different models of spiral structure in the Milky Way
\citep{2019MNRAS.tmp..155S}. Characteristics of the distribution of stars in the extended Solar neighborhood in action space are discussed in
\citet{2018arXiv180503653T}.

@@

\subsection{The size of the Solar neighborhood} \label{sssec:neighborhood}
Given a local coordinate system, the amplitude and characteristic length scale
of the density fluctuations in the Galactic disk will determine how far this
system can be extended before introducing $\mathcal{O}(1)$ systematic errors
in the computation of actions for thin-disk stars. We consider this a
criterion for the region around the Sun where the analysis of the action-space
distribution of stars on quasi-circular orbits, and therefore the epicyclic
approximation, can be expected to be valid. This leads to a somewhat
dynamically motivated definition of the ``solar neighborhood.'' Since the
motivation may be different for defining the solar neighborhood in, e.g.,
studies of the chemical distribution of the Galaxy, we propose the phrase
``dynamical solar neighborhood.''

>>>>

If the system being considered departs from axisymmetry in a significant and/or non-adiabatic way, the actions computed using an axisymmetric approximation to the true potential can exhibit cyclic dependence on the orbital phase (or time at which the star's position and velocity are observed), large-scale migration, or diffusion from their initial values.
In the Milky Way, stellar actions are expected to diffuse on short time scales due to scattering with gas clouds
and to evolve on longer time scales in the case of orbits near resonances with spiral arms, bar(s), and other
large scale perturbations \citep{2014RvMP...86....1S}. For this reason, we and
other authors have used actions to study stellar scattering in the Milky Way
disk using the improved astrometry of {\em Gaia} DR2 and various age
catalogues \citep{2018ApJ...867...31B,2018arXiv180803278T}. Actions have also
been used to study different models of spiral structure in the Milky Way
\citep{2019MNRAS.tmp..155S}. Characteristics of the distribution of stars in the extended solar neighborhood in action space are discussed in
\citet{2018arXiv180503653T}.

@@

\subsection{The size of the solar neighborhood} \label{sssec:neighborhood}
Given a local coordinate system, the amplitude and characteristic length scale
of the density fluctuations in the Galactic disk will determine how far this
system can be extended before introducing $\mathcal{O}(1)$ systematic errors
in the computation of actions for thin-disk stars. We consider this a
criterion for the region around the Sun where the analysis of the action-space
distribution of stars on quasi-circular orbits, and therefore the epicyclic
approximation, can be expected to be valid. This leads to a somewhat
dynamically motivated definition of the ``solar neighborhood.'' Since the
motivation may be different for defining the solar neighborhood in, e.g.,
studies of the chemical distribution of the Galaxy, we propose the phrase
``dynamical solar neighborhood.''
